Supporting Ecological Decision Making Using Feature-Selection and Variable Importance

### 2019-08-31 code/98-paper/ieee/ieee-manuscript.tex
update methods section with feature imp

\noindent An exhaustive hyperparameter tuning was applied during nested spatial \ac{CV} for all algorithms.
Maximum Bayesian Optimization \cite{mlrmbo} was used for parameter optimization.
This approach first composes \textit{n} randomly chosen hyperparameter settings out of a user defined search space.
After these \textit{n} tries have been evaluated, a new hyperparameter setting, which is going to be evaluated next, is proposed based on a fitted regression model.
The regression model estimates the performance of the machine-learning method for unknown hyperparameter settings.
Using these estimates, a new promising hyperparameter setting is proposed to be evaluated next.
This strategy continues until a termination criterion, defined by the user, is reached \cite{hutter2011, jones1998}.
An initial design of 30 randomly composed hyperparameter settings and a termination criterion of 70 iterations was used, resulting in a total budget of 100 evaluated hyperparameter settings per fold.
The advantage of this tuning approach is the substantial reduction of the tuning budget required to find a setting which is close to the global minimum
This applies when being compared to methods that do not use information from previous runs, such as random search or grid search \cite{bergstra2012}.

@@

\subsection{Calculation of model feature importance}
\noindent A permutation-based feature importance estimation was done for the best algorithm of each feature set and filter method, respectively.
This method caluclates the loss of predictive performance for each feature by permuting it in a random manner.
The more important the feature is for the model, the higher the loss in the used error measure will be, reflecting the importance of the specific feature for the current model.

@@

\begin{figure} [t!]
\centering
	\begin{center}
		\includegraphics[width=0.5\textwidth] {performance-results-1.pdf}
        \caption{Scored predictive performance (RMSE) of models across tasks. Prefix "CV" denotes that the learner was optimized using internal 10-fold CV while prefix "MBO" means that Bayesian optimization was used for hyperparameter optimization. The abbreviations on the y-axis refer to the combinations of feature sets on which each model was scored on. Labels attached to each point in space show which filter method was used for scoring features during the feature selection process (NF = no filter, Car = "Carscore", Info = "Information Gain", Borda = "Borda"). The second value in the attached label of each point shows the scored RMSE value of the respective setting.}
		\label{fig:perf-result}
	\end{center}
\end{figure}
\section{Discussion}

>>>>

\noindent An exhaustive hyperparameter tuning was applied during nested spatial \ac{CV} for all algorithms.
Maximum Bayesian Optimization \cite{mlrmbo} (MBO) was used for parameter optimization.
This approach first composes \textit{n} randomly chosen hyperparameter settings out of a user defined search space.
After these \textit{n} tries have been evaluated, a new hyperparameter setting, which is going to be evaluated next, is proposed based on a fitted regression model.
The regression model estimates the performance of the machine-learning method for unknown hyperparameter settings.
Using these estimates, a new promising hyperparameter setting is proposed to be evaluated next.
This strategy continues until a termination criterion, defined by the user, is reached \cite{hutter2011, jones1998}.
An initial design of 30 randomly composed hyperparameter settings and a termination criterion of 70 iterations was used, resulting in a total budget of 100 evaluated hyperparameter settings per fold.
The advantage of this tuning approach is the substantial reduction of the tuning budget required to find a setting which is close to the global minimum
This applies when being compared to methods that do not use information from previous runs, such as random search or grid search \cite{bergstra2012}.
In addition to MBO, the penalization term of Lasso and Ridge was optimized using the internal non-spatial CV approach due to promising results in other applications.

@@

\subsection{Calculation of model feature importance}
\noindent A permutation-based feature importance estimation was conducted for the best algorithm of each feature set and filter method, respectively.
This method calculates the loss of predictive performance for each feature by permuting it in a random manner.
The more important the feature is for the model, the higher the loss in the used error measure will be, reflecting the importance of the specific feature for the current model.
To balance both runtime and variance reduction, we opted for 25 iterations of each feature permutation.

@@

\begin{figure} [t!]
\centering
	\begin{center}
		\includegraphics[width=0.5\textwidth] {performance-results-1.pdf}
        \caption{Scored predictive performance (RMSE) of models across tasks. Prefix "CV" denotes that the learner was optimized using internal 10-fold CV while prefix "MBO" means that Bayesian optimization was used for hyperparameter optimization. The abbreviations on the y-axis refer to the combinations of feature sets on which each model was scored on. Labels attached to each point in space show which filter method was used for scoring features during the feature selection process (NF = no filter, Car = "Carscore", Info = "Information Gain", Borda = "Borda"). The second value in the attached label of each point shows the scored RMSE value of the respective setting.}
		\label{fig:perf-result}
	\end{center}
\end{figure}

\subsection{Permutation-based variable importance}
\section{Discussion}
